A parametric system for adaptive extrusion width contour parallel toolpath generation

### 2019-08-20 4_method.tex
lil

\subsection{Bead counts}
We assign a bead count to each node in the skeleton which is in `the center' of the shape in a sense to be defined below.
Around regions where the bead count changes we introduce transition regions, so that we can smoothly change between regions with different bead count.

>>>>

\subsection{Bead counts}
We assign a bead count to each node in the skeleton which is in `the center' of the shape in a sense which will be defined in \cref{sec:significance_measure}.
Around regions where the bead count changes we introduce transition regions, so that we can smoothly change between regions with different bead count.
